Cultural Transmission and Technological Transitions during the Late Paleolithic in Korea

### 2023-02-14 analysis/paper/paper.qmd
renv

One limitation of this aggregation of all stemmed points in our sample into each chronological phase is that the sample consists of a relatively large number of assemblages with only 1-2 stemmed points. These isolated finds are ambiguous with respect to a local tradition of artifact making, so to further investigate temporal change, we focus only the four assemblages that have more than five stemmed points (@fig-plot-cor-four-assemblage). We assume these four assemblages are more likely to represent a consistent, recurring way of making stemmed points than isolated finds, and thus more relevant for comparing modes of cultural transmission of artifact making. The four assemblages include three from Suyanggae (SYG) and one from Yongsandong (YS). There are more variation in correlation coefficient in Phase 2 while the median values for the two assemblages from Phase 3 are similar to each other and close to `r threshold_value_cor`. There is no clear pattern between assemblages. SYG1_2 is from Phase 2 but it has the higher median than the assemblage from the same site in the later phase.

>>>>

One limitation of this aggregation of all stemmed points in our sample into each chronological phase is that the sample consists of a relatively large number of assemblages with only 1-2 stemmed points. These isolated finds are ambiguous with respect to a local tradition of artifact making, so to further investigate temporal change, we focus only the four assemblages that have more than five stemmed points (@fig-plot-cor-four-assemblage). We assume these four assemblages are more likely to represent a consistent, recurring way of making stemmed points than isolated finds, and thus more relevant for comparing modes of cultural transmission of artifact making. The four assemblages include three from Suyanggae (SYG) and one from Yongsandong (YS). There is more variation in correlation coefficients in Phase 2 while the median values for the two assemblages from Phase 3 are similar to each other and close to `r threshold_value_cor`. There is no clear pattern between assemblages. SYG1_2 is from Phase 2 but it has the higher median than the assemblage from the same site in the later phase.
